### 2021-08-13 paper/paper.tex
Remove superfluous "often"
Introduce "Pkg" as the package manager name

Many scientists implementing numerical methods often have no formal training
in software development. Julia and its ecosystem support these
researchers by making it easy to set up unit and regression tests, since a
testing framework is included in the standard library. This facilitates test-driven
development and continuous integration (CI), which makes code restructuring
and optimization straightforward.

@@

In addition, the package manager fosters a unified form of semantic versioning
across the Julia ecosystem, which lays the basis for the following three
observations.

@@

The package manager makes it easy to reproduce the exact runtime environment, including
binary dependencies, used to generate numerical results. We have used this feature for all of our papers based on
\trixi \cite{schlottkelakemper2021purely, ranocha2021preventing}, including this
one \cite{ranocha2021adaptiveRepro}.
This facilitates code sharing and reproducible research in computational science,
which is arguably important but not yet mainstream \cite{barnes2010publish,
donoho2010invitation, leveque2013top}.

>>>>

Many scientists implementing numerical methods have no formal training
in software development. Julia and its ecosystem support these
researchers by making it easy to set up unit and regression tests, since a
testing framework is included in the standard library. This facilitates test-driven
development and continuous integration (CI), which makes code restructuring
and optimization straightforward.

@@

In addition, the Julia package manager \lstinline{Pkg} fosters a unified form of semantic versioning
across the Julia ecosystem, which lays the basis for the following three
observations.

@@

The package manager \lstinline{Pkg} makes it easy to reproduce the exact runtime environment, including
binary dependencies, used to generate numerical results. We have used this feature for all of our papers based on
\trixi \cite{schlottkelakemper2021purely, ranocha2021preventing}, including this
one \cite{ranocha2021adaptiveRepro}.
This facilitates code sharing and reproducible research in computational science,
which is arguably important but not yet mainstream \cite{barnes2010publish,
donoho2010invitation, leveque2013top}.
